### 2011-06-15 thesis/introduction.tex
Semantic Mapping chapter almost finished.

\chapter{Introduction}
% Introduce:
%  Mobile Robotics, A.I.
%  Interaction with Humans
%  Need for concepts/semantic information
%  Dynamic human environment
%  Non-feasibility of hard-coded concepts
%  Requirements to detect novelty and handle it.
For a long time humanity has fantasized that one day robots will walk among us.
They will move and be able to interact with us. Understand our concepts and
be able to reason.

>>>>

\chapter{Introduction}
There has been several efforts in the areas of artificial intelligence and robotics
in creating robots that are able to interact with humans and their environments.
One of the important aspects is to endow those robots with a deeper understanding
of human environments, not just for the purpose of navigation and obstacle avoidance, 
but also in terms of human semantics and functionality.

In that sense the need for semantic mapping arises, and it can be described as the
relation between spatial areas and a set of existent concepts used by humans to
describe them.

An essential competence for cognitives robots is their ability to reason about space.
Spatial knowledge plays an important role in navigation, reasoning, planning and episodic memory.

% Introduce:
%  Mobile Robotics, A.I.
%  Interaction with Humans
%  Need for concepts/semantic information
%  Dynamic human environment
%  Non-feasibility of hard-coded concepts
%  Requirements to detect novelty and handle it.
For a long time humanity has fantasized that one day robots will walk among us.
They will move and be able to interact with us. Understand our concepts and
be able to reason.

### 2011-06-15 thesis/semantic-mapping.tex
Semantic Mapping chapter almost finished.

% motivation
Humans associate concepts to areas that relate to the functionality of those. That
association is either useful by explaining where to find certain objects as well to
understand the types of activities to perform on it. In a

Those human-concepts are meant to be meaningful for humans and by incorporating conceptual
knowledge about them it is expected to improve the agent 
% semantic mapping definition
In this context semantic mapping is seen as the process of building a representation of
the environment which associates spatial entities with a set of defined spatial concepts (i.e.\ human concepts).

% importance of conceptual knowledge
% application of conceptual knowledge
It is expected that by being able to reason over those semantics an agent can better
understand human environments and increase its efficiency when performing human-tasks on them.
By handling this conceptual knowledge the agent becomes aware of

% challenges and need for representing uncertainty
The goal of a spatial representation is to provide the agent with a view about the environment
that allows it to reason beyond its sensory horizon.

 Such a representation is by its nature
imperfect, incomplete, inaccurate and invalid.

world that allows the agent to perform reasoning over it and efficiently perform tasks.
It should also give the agent ability to reason about parts 
Such a representation cannot be perfect since the methods and information are uncertain

% here a here a method is used that does semantic mappping and representes conceptual knowledge
% on a probabilistic fashion.

It is therefore clear that the need to handle information on an high-level semantic and
probabilistic fashion arises not only for efficiency reasons but also from the desire
of being able to communicate and reason on those aspects.
In order to fully explore the semantic properties and their relations it is necessary to
detect and classify semantic aspects as well to understand the relationships between them.
That conceptual knowledge is important and any limitations on it will limit the capacities
of an agent to reason.

This thesis motivation lies on developing methods for detecting knowledge gaps
on the semantic knowledge of a mobile agent. For that the semantic mapping system
implemented on \gls{Dora} proposed by \cite{pronobis2011phd} was used as a base.

@@

Besides that the spatial knowledge representation has been drawn with an high-focus on probabilistic
and uncertain reasoning, human interaction and life-long learning capabilities.
For that it was considered an excellent base defining not only the concepts and
requirements of an high-level semantic representation but also the information flow
between all the layers involved on the agent.

Being able to perform probabilistic inference on all available information Such a representation is suitable to detect novel concepts.

The system is implemented on \Gls{Dora} and a brief overview of its architecture is
given in the following sections.

>>>>

% motivation
Humans associate concepts to areas that relate to the functionality of those. That
association is either useful by explaining where to find certain objects as well to
understand the types of activities to perform on it. 
Those human-concepts are meant to be meaningful for humans and by incorporating conceptual
knowledge about them it is expected to improve the agent ability to interact and communicate
with humans and the ability perform human-like tasks.

% semantic mapping definition
In this context semantic mapping is seen as the process of building a representation of
the environment which associates spatial entities with a set of defined spatial concepts (in this case the human concepts).

Missing:
\begin{itemize}
\item importance of conceptual knowledge
% In order to build such a mapping of the environment, it is important to define the knowledge that allows the agent to reason
% about.

\item application of conceptual knowledge
% It is expected that by being able to reason over those semantics an agent can better
% understand human environments and increase its efficiency when performing human-tasks on them.
% By handling this conceptual knowledge the agent becomes aware of

\item challenges and need for representing uncertainty
% The goal of a spatial representation is to provide the agent with a view about the environment
% that allows it to reason beyond its sensory horizon.

% Such a representation is by its nature imperfect, incomplete, inaccurate and invalid.

% world that allows the agent to perform reasoning over it and efficiently perform tasks.
% It should also give the agent ability to reason about parts 
% Such a representation cannot be perfect since the methods and information are uncertain

% It is therefore clear that the need to handle information on an high-level semantic and
% probabilistic fashion arises not only for efficiency reasons but also from the desire
% of being able to communicate and reason on those aspects.
% In order to fully explore the semantic properties and their relations it is necessary to
% detect and classify semantic aspects as well to understand the relationships between them.
% That conceptual knowledge is important and any limitations on it will limit the capacities
% of an agent to reason. 
\end{itemize}

% here a here a method is used that does semantic mappping and representes conceptual knowledge
% on a probabilistic fashion.
This thesis motivation lies on developing methods for detecting knowledge gaps on the spatial
semantic knowledge of a mobile agent. For that spatial knowledge needs to be defined, as well
the methods used to perform the semantic mapping.
In that context this chapter presents \gls{Dora}, a system that represents its spatial knowledge
with the representation proposed by \cite{pronobis2010ias}, and performs semantic mapping using
inference on a probabilistic graphical model.

@@

The \emph{spatial knowledge representation} has been drawn with an high-focus on probabilistic
and uncertain reasoning, human interaction and life-long learning capabilities.
For that it was considered an excellent base defining not only the concepts and
requirements of an high-level semantic representation but also the information flow
between all the layers involved on the agent.

\gls{Dora}, the system, utilizes its spatial knowledge to perform semantic mapping of the environment
using probabilist inferences on top of a graphical model.
Due to its nature, it was considered suitable for implementing novelty detection of semantic concepts.
